---
title: "Tea first or milk first? Doesn't matter!"
author: 
  - Jayden Jung
  - Jason Ngo
  - Iz Leitch
  - Randall Ni
  - Julie Nguyen
  - Will Davidson
  - Syed Hassan
  - Tayedza Chikumbirike
thanks: "Code and data are available at: https://github.com/tayedzac/tea_tasting"
date: "`r Sys.time()`"
date-format: "MMMM D YYYY"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# Data {#sec-data}

For this experiment we collected our own data exploring whether it is possible to taste the difference between tea first or milk first. Along the way we had some challenges, we had trouble getting exact measurements as the scale could only measure within .5 of a gram. There was also the issue of the cups not being stirred. Lastly, the tester both doesn't normally drink tea but also has a diet without subtle flavours.

```{r}
#| echo: false
#| warning: false
#| message: false

tea_data <- read_csv(here::here("inputs/data/raw_data.csv"), 
                     show_col_types = FALSE)

tea_data %>% 
  ggplot(aes(x = group, fill = type)) +
  geom_bar() +
  labs(x = "Grouping by subject", y = "Count", fill = "Cup type") + 
  ggtitle("The subject could not discern at all the two types") 
```

# Results

The results were highly conclusive pointing to no difference between milk first and tea first, as there was a 50/50 distribution in the tester made groups.

## Weaknesses and next steps

In next steps, we would use a simpler method for adding the milk, such as a measuring scoop, as this would keep the amounts similar without having to use a scale. We would also like to compare the tasting ability across different testers with different tea experience levels and diets. We would also like to control for other factors such as temperature, and steeping level, as some samples were warmer than others affecting the taste. As well, a larger amount of tea allowing for better testing.
